Analysis of competitive surfing tournaments with generalized Bradley-Terry likelihoods

### 2022-09-25 inst/surfing_jsa.tex
fixes #175

\documentclass{article}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{diagbox}
\usepackage[pdftex]{hyperref}

@@

\begin{table}[h]
\begin{tabular}{llllllllllllll}
competitor  & nationality&WCT01  &WCT02  &WCT03  & \ldots  &WCT10&WCT11&points\\ \hline
 Ferreira   &   BRA      &   1   &   5   &   17  & \ldots  &   1   &   1   &   59740\\
 Medina     &   BRA      &   5   &   5   &   17  & \ldots  &   9   &   2   &   56475\\
 Smith 	    &   ZAF      &   3   &   3   &   17  & \ldots  &   2   &   17  &   49985\\
 Toledo     &   BRA      &   9   &   2   &   5   & \ldots  &   5   &   17  &   49145\\
 Andino     &   USA      &   2   &   17  &   5   & \dots   &   5   &   9   &   46655\\
 $\vdots$   &            &   &   &       &       & $\vdots$&       &       &
\end{tabular}
\caption{Conventional league table for the top five competitors in WSL
  2019 tour. \label{resultstable} Thus at WCT01 (Coolangatta, QLD) we see
  Ferreira coming first, Andino second and Smith third}
\end{table}

>>>>

\documentclass{article}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{diagbox}
\usepackage{multirow}
\usepackage[pdftex]{hyperref}

@@

% use   \begin{tabular}{@{}c@{}}\small{WCT} \\ 01\end{tabular} for WCT\\01
\begin{table}[h]
\begin{tabular}{llllllllllllll}
competitor  & nationality & \multirow{ 5}{*}{1} &  &  & WCT & & &points\\
            &             &  01   & 02& 03& \ldots& 10 & 11 & \\ \hline
 Ferreira   &   BRA       &   1   &   5   &   17  & \ldots  &   1   &   1   &   59740\\
 Medina     &   BRA       &   5   &   5   &   17  & \ldots  &   9   &   2   &   56475\\
 Smith 	    &   ZAF       &   3   &   3   &   17  & \ldots  &   2   &   17  &   49985\\
 Toledo     &   BRA       &   9   &   2   &   5   & \ldots  &   5   &   17  &   49145\\
 Andino     &   USA       &   2   &   17  &   5   & \dots   &   5   &   9   &   46655\\
 $\vdots$   &             &   &   &       &       & $\vdots$&       &       &
\end{tabular}
\caption{Conventional league table for the top five competitors in WSL
  2019 tour. \label{resultstable} Thus at WCT01 (Coolangatta, QLD) we see
  Ferreira coming first, Andino second and Smith third}
\end{table}
